Draft

### 2023-04-18 Draft.Rmd
load libraries

---
title: "Draft"
author: "Aileen Li"
date: "2023-04-18"
output: html_document
---

@@

```{r}
library(tidyverse)
dat <- read_csv("https://github.com/rdpeng/stat322E_public/raw/main/data/pm25_data.csv.gz")

>>>>

---
title: "Draft"
author: "Aileen Li, Nyah Strickland"
date: "2023-04-18"
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

```{r}
library(tidyverse)
library(tidymodels)
library(broom)
library(carat)
library(randomForest)
library(plotROC)

origin <- read_csv("https://github.com/rdpeng/stat322E_public/raw/main/data/pm25_data.csv.gz")
